---
title: "pvs_analysis_report"
output: html_document
---

```{r echo=FALSE}

# loading packages

if(!require(pacman)) install.packages("pacman")

p_load(
  tidyverse,
  here,
  summarytools,
  janitor,
  sf, 
  tmap,
  OpenStreetMap,
  flextable,
  rio, 
  gtsummary, 
  epikit, 
  gt
)


# loading data


 pvs_data<- import(
  here(
    "data/Malawi_PVS_data_.dta"
  )) |> 
   mutate(
    across(where(is.character), as.factor)
  )  |>as_tibble()
 

  



```

# Descriptive 

## Demographic by person

under this section the demographic variable will be analyzed by mode of data collection. face to face or via phone interviews.

Format 1 

```{r echo=FALSE}

demo_df1 <-  pvs_data |> 
  select(
    mode, 
    ageband, 
    q3,
    q8, 
    q8a, 
    q8b
  )

demo_df1 |> 
  tbl_summary(
    by = mode, 
    missing = "no", 
    digits = list(
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      ageband ~ "Age Band",
      q3 ~ "Sex",
      q8 ~ "Education",
      q8a ~ "Ethincity",
      q8b ~ "Income Level"
    )
  )


```

Format 2


```{r echo=FALSE}

demo_df1 |> 
  tbl_summary(
    missing = "no", 
    digits = list(
      
      mode~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      
      mode~ "Mode of Data Collection",
      ageband ~ "Age Band",
      q3 ~ "Sex",
      q8 ~ "Education",
      q8a ~ "Ethincity",
      q8b ~ "Income Level"
    )
  )


```


# Demographic by place

under this section the demographic variable will be analyzed by mode of data collection. face to face or via phone interviews. focus on district, region and residence.

format 1

```{r echo=FALSE}

demo_df2 <- pvs_data |> 
  select(
    mode, 
    q4,
    q4_1,
    q5
  )

demo_df2 |>
  tbl_summary(
    by = mode, 
    missing = "no", 
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4 ~ "Region",
      q4_1 ~ "District",
      q5 ~ "Residence"
    )
  )

```

format 2

```{r echo=FALSE}

demo_df2 |>
  tbl_summary(
   missing = "no", 
    digits = list(
      mode ~ c(0, 2),
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      mode ~ "Mode of Data Collection",
      q4 ~ "Region",
      q4_1 ~ "District",
      q5 ~ "Residence"
    )
  )

```

# crosstabs of demographic variables and type of health facility: 
was this a public or private health facility? Q32 by demographic of person. 

```{r echo=FALSE}


q32_df<- pvs_data |> 
  select(
    mode, 
    q32, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q32_df |>
  tbl_summary(
    by=q32, 
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ), 
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~ "Sex", 
      q8~ "Education",
      q8a~"Ethinicity",
      q8b~ "Income Level"
    )
  ) 
  
  
```


was this a public or private health facility? Q32 by demographic of district, residence and region.

```{r echo=FALSE}

q32_df2<- pvs_data |> 
  select(
    mode, 
    q32, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q32_df2 |>
  tbl_summary(
    by=q32, 
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ), 
    label = list(
      mode~ "Mode of data collection",
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  )


```

# crosstabs of demographic variables and staying overnight at health facility:

in the past 12 month did you stay overnight? q26 by demographic of person.

```{r echo=FALSE}
q26_df<- pvs_data |> 
  select(
    mode, 
    q26, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )

q26_df |>
  tbl_summary(
    by= q26,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity", 
      q8b~ "Income Level"
    )
      )


```

# in the past 12 month did you stay overnight? q26 by demographic of district, residence and region.

```{r echo=FALSE}

q26_df2<- pvs_data |> 
  select(
    q26, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )

q26_df2 |>
  tbl_summary(
    by= q26,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  )



```

# crosstabs of demographic variable number 3

## q27a demographic variabel of person

```{r echo=FALSE}
q27a_df<- pvs_data |> 
  select(
    mode, 
    q27a, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )

q27a_df |>
  tbl_summary(
    by= q27a,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex",
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Have you had your blood pressure measured from any healthcare provider"
  )

```

## q27a demographic variabel of district, residence and region

```{r echo=FALSE}
q27a_df2<- pvs_data |> 
  select(
    q27a, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q27a_df2 |>
  tbl_summary(
    by= q27a,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Have you had your blood pressure measured from any healthcare provider"
  )

```

## q27b demographic variabel of person

```{r echo=FALSE}
q27b_df<- pvs_data |> 
  select(
    mode, 
    q27b, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q27b_df |>
  tbl_summary(
    by= q27b,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Have you received a mammogram from any healthcare provider"
  )

```


## q27b demographic variabel of district, residence and region

```{r}
q27b_df2<- pvs_data |> 
  select(
    q27b, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q27b_df2 |>
  tbl_summary(
    by= q27b,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Have you received a mammogram from any healthcare provider"
  )
  
  
  
  
```

## q27c demographic variabel of person


```{r echo=FALSE}

q27c_df<- pvs_data |> 
  select(
    mode, 
    q27c, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )




q27c_df|>
  filter(q3=="Female")|> 
  select(-q3) |>
  tbl_summary(
    by= q27c,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode ~ "Mode of data collection",
      ageband ~ "Age Band",
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  )
  
  
  
  
  
  
  

```

