---
title: "pvs_analysis_report"
output: html_document
---

```{r echo=FALSE}

# loading packages

if(!require(pacman)) install.packages("pacman")

p_load(
  tidyverse,
  here,
  summarytools,
  janitor,
  sf, 
  tmap,
  OpenStreetMap,
  flextable,
  rio, 
  gtsummary, 
  epikit, 
  gt
)


# loading data


 pvs_data<- import(
  here(
    "data/Malawi_PVS_data_.dta"
  )) |> 
   mutate(
    across(where(is.character), as.factor)
  )  |>as_tibble()
 

```

# Descriptive 

## Demographic by person

under this section the demographic variable will be analyzed by mode of data collection. face to face or via phone interviews.

Format 1 

```{r echo=FALSE}

demo_df1 <-  pvs_data |> 
  select(
    mode, 
    ageband, 
    q3,
    q8, 
    q8a, 
    q8b
  )

demo_df1 |> 
  tbl_summary(
    by = mode, 
    missing = "no", 
    digits = list(
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      ageband ~ "Age Band",
      q3 ~ "Sex",
      q8 ~ "Education",
      q8a ~ "Ethincity",
      q8b ~ "Income Level"
    )
  )


```

Format 2


```{r echo=FALSE}

demo_df1 |> 
  tbl_summary(
    missing = "no", 
    digits = list(
      
      mode~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      
      mode~ "Mode of Data Collection",
      ageband ~ "Age Band",
      q3 ~ "Sex",
      q8 ~ "Education",
      q8a ~ "Ethincity",
      q8b ~ "Income Level"
    )
  )


```


# Demographic by place

under this section the demographic variable will be analyzed by mode of data collection. face to face or via phone interviews. focus on district, region and residence.

format 1

```{r echo=FALSE}

demo_df2 <- pvs_data |> 
  select(
    mode, 
    q4,
    q4_1,
    q5
  )

demo_df2 |>
  tbl_summary(
    by = mode, 
    missing = "no", 
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4 ~ "Region",
      q4_1 ~ "District",
      q5 ~ "Residence"
    )
  )

```

format 2

```{r echo=FALSE}

demo_df2 |>
  tbl_summary(
   missing = "no", 
    digits = list(
      mode ~ c(0, 2),
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      mode ~ "Mode of Data Collection",
      q4 ~ "Region",
      q4_1 ~ "District",
      q5 ~ "Residence"
    )
  )

```

# crosstabs of demographic variables and type of health facility: 
was this a public or private health facility? Q32 by demographic of person. 

```{r echo=FALSE}


q32_df<- pvs_data |> 
  select(
    mode, 
    q32, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q32_df |>
  tbl_summary(
    by=q32, 
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ), 
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~ "Sex", 
      q8~ "Education",
      q8a~"Ethinicity",
      q8b~ "Income Level"
    )
  ) 
  
  
```


was this a public or private health facility? Q32 by demographic of district, residence and region.

```{r echo=FALSE}

q32_df2<- pvs_data |> 
  select(
    mode, 
    q32, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q32_df2 |>
  tbl_summary(
    by=q32, 
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ), 
    label = list(
      mode~ "Mode of data collection",
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  )


```

# crosstabs of demographic variables and staying overnight at health facility:

in the past 12 month did you stay overnight? q26 by demographic of person.

```{r echo=FALSE}
q26_df<- pvs_data |> 
  select(
    mode, 
    q26, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )

q26_df |>
  tbl_summary(
    by= q26,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity", 
      q8b~ "Income Level"
    )
      )


```

# in the past 12 month did you stay overnight? q26 by demographic of district, residence and region.

```{r echo=FALSE}

q26_df2<- pvs_data |> 
  select(
    q26, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )

q26_df2 |>
  tbl_summary(
    by= q26,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  )



```

# crosstabs of demographic variable number 3

## q27a demographic variabel of person

```{r echo=FALSE}
q27a_df<- pvs_data |> 
  select(
    mode, 
    q27a, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )

q27a_df |>
  tbl_summary(
    by= q27a,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex",
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Have you had your blood pressure measured from any healthcare provider"
  )

```

## q27a demographic variabel of district, residence and region

```{r echo=FALSE}
q27a_df2<- pvs_data |> 
  select(
    q27a, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q27a_df2 |>
  tbl_summary(
    by= q27a,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Have you had your blood pressure measured from any healthcare provider"
  )

```

## q27b demographic variabel of person

```{r echo=FALSE}
q27b_df<- pvs_data |> 
  select(
    mode, 
    q27b, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q27b_df |>
  tbl_summary(
    by= q27b,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Have you received a mammogram from any healthcare provider"
  )

```


## q27b demographic variabel of district, residence and region

```{r}
q27b_df2<- pvs_data |> 
  select(
    q27b, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q27b_df2 |>
  tbl_summary(
    by= q27b,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Have you received a mammogram from any healthcare provider"
  )
  
  
  
  
```

## q27c demographic variabel of person

```{r echo=FALSE}

q27c_df<- pvs_data |> 
  select(
    mode, 
    q27c, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )




q27c_df|>
  filter(q3=="Female")|> 
  select(-q3) |>
  tbl_summary(
    by= q27c,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode ~ "Mode of data collection",
      ageband ~ "Age Band",
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  )
  
  

```

## q27c demographic variabel of district, residence and region

```{r}

q27c_df2<- pvs_data |> 
  select(
    q27c, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q27c_df2 |> 
  tbl_summary(
    by= q27c,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |>
  modify_caption(
    "Have you received cervical cancer screening from any healthcare provide"
  )
  
  
  
  
  
```

## q27d Q27d. Have you had your eyes or vision checked from any healthcare provide. 

```{r}
q27d_df 

```

##Objective 4
## Q42. Overall, how would you rate the quality of the government or public healthcare system in Malawi? Please answer even if you have not used these services.
## q42 demographic variabel of person

```{r echo=FALSE}
q42_df<- pvs_data |> 
  select(
    mode, 
    q42, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q42_df |>
  tbl_summary(
    by= q42,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Quality of  faith-based or NGO healthcare system in Malawi"
  )

```


## q42 demographic variabel of district, residence and region

```{r}
q42_df2<- pvs_data |> 
  select(
    q42, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q42_df2 |>
  tbl_summary(
    by= q42,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Quality of  faith-based or NGO healthcare system in Malawi"
  )
```
## Q43. Overall, how would you rate the quality of the private for-profit healthcare system in Malawi
## q43 demographic variabel of person

```{r echo=FALSE}
q43_df<- pvs_data |> 
  select(
    mode, 
    q43, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q43_df |>
  tbl_summary(
    by= q43,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Quality of the private for-profit healthcare system in Malawi"
  )

```


## q43 demographic variabel of district, residence and region

```{r}
q43_df2<- pvs_data |> 
  select(
    q43, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q43_df2 |>
  tbl_summary(
    by= q43,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Quality of the private for-profit healthcare system in Malawi"
  )
  
```
## Q44. Overall, how would you rate the quality of  faith-based or NGO healthcare system in Malawi
## q44 demographic variabel of person

```{r echo=FALSE}
q44_df<- pvs_data |> 
  select(
    mode, 
    q44, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q44_df |>
  tbl_summary(
    by= q44,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Quality of  faith-based or NGO healthcare system in Malawi"
  )

```


## q44 demographic variabel of district, residence and region

```{r}
q44_df2<- pvs_data |> 
  select(
    q44, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q44_df2 |>
  tbl_summary(
    by= q44,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Quality of  faith-based or NGO healthcare system in Malawi"
  )
 ```
##Objective 5
## Q45. Thinking about the past two years, would you say Malawi’s health system is getting better, staying the same, or getting worse
## q45 demographic variabel of person

```{r echo=FALSE}
q45_df<- pvs_data |> 
  select(
    mode, 
    q45, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q45_df |>
  tbl_summary(
    by= q45,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Would you say Malawi’s health system is getting better, staying the same, or getting worse"
  )

```


## q45 demographic variabel of district, residence and region

```{r}
q45_df2<- pvs_data |> 
  select(
    q45, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q45_df2 |>
  tbl_summary(
    by= q45,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Would you say Malawi’s health system is getting better, staying the same, or getting worse"
  )
  ```
##Objective 5
##Q46. Which of the following statements do you agree with most
##q46 demographic variabel of person

```{r echo=FALSE}
q46_df<- pvs_data |> 
  select(
    mode, 
    q46, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q46_df |>
  tbl_summary(
    by= q46,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Q46. Which of the following statements do you agree with most"
  )

```


## q46 demographic variabel of district, residence and region

```{r}
q46_df2<- pvs_data |> 
  select(
    q46, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q46_df2 |>
  tbl_summary(
    by= q46,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Which of the following statements do you agree with most"
  )
```
##Q47. How would you rate the government’s management of the COVID-19 pandemic overall
##q47 demographic variabel of person

```{r echo=FALSE}
q47_df<- pvs_data |> 
  select(
    mode, 
    q47, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )



q47_df |>
  tbl_summary(
    by= q47,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Rate the government’s management of the COVID-19 pandemic overall"
  )

```


## q47 demographic variabel of district, residence and region

```{r}
q47_df2<- pvs_data |> 
  select(
    q47, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q47_df2 |>
  tbl_summary(
    by= q47,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Rate the government’s management of the COVID-19 pandemic overall"
  )
```

## Q48. How would you rate the government’s management of the Cholera outbreak overall
##q48 demographic variabel of person

```{r echo=FALSE}
q48_df<- pvs_data |> 
  select(
    mode, 
    q48, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q48_df |>
  tbl_summary(
    by= q48,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "Rate the government’s management of the COVID-19 pandemic overall"
  )

```


## q48 demographic variabel of district, residence and region

```{r}
q48_df2<- pvs_data |> 
  select(
    q48, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q48_df2 |>
  tbl_summary(
    by= q48,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "Rate the government’s management of the Cholera outbreak overall"
  )
```
##Q41a. How confident are you that you would receive good quality healthcare if you became very sick
##q41a demographic variabel of person

```{r echo=FALSE}
q41a_df<- pvs_data |> 
  select(
    mode, 
    q41a, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q41a_df |>
  tbl_summary(
    by= q41a,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "How confident are you that you would receive good quality healthcare if you became very sick"
  )

```

## q41a demographic variabel of district, residence and region

```{r}
q41a_df2<- pvs_data |> 
  select(
    q41a, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q41a_df2 |>
  tbl_summary(
    by= q41a,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "How confident are you that you would receive good quality healthcare if you became very sick"
  )
 ```
## Q41b. How confident are you that you would be able to afford the healthcare you needed if you became very sick
##q41b demographic variabel of person

```{r echo=FALSE}
q41b_df<- pvs_data |> 
  select(
    mode, 
    q41b, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q41b_df |>
  tbl_summary(
    by= q41b,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "How confident are you that you would be able to afford the healthcare you needed if you became very sick"
  )

```

## q41b demographic variabel of district, residence and region

```{r}
q41b_df2<- pvs_data |> 
  select(
    q41b, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q41b_df2 |>
  tbl_summary(
    by= q41b,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "How confident are you that you would be able to afford the healthcare you needed if you became very sick"
  )
 ```
##Q41c. How confident are you that the government considers the public’s opinion when making decisions about the healthcare system
##q41c demographic variabel of person

```{r echo=FALSE}
q41c_df<- pvs_data |> 
  select(
    mode, 
    q41c, 
    ageband, 
    q3, 
    q8, 
    q8a, 
    q8b
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q41c_df |>
  tbl_summary(
    by= q41c,
    missing = "no",
    digits = list(
      mode ~ c(0, 2),
      ageband ~ c(0, 2),
      q3 ~ c(0, 2),
      q8 ~ c(0, 2), 
      q8a ~ c(0, 2), 
      q8b ~ c(0, 2)
    ),
    label = list(
      mode~ "Mode of data collection",
      ageband ~ "Age Band",
      q3~"Sex", 
      q8~ "Education",
      q8a~ "Ethinicity",
      q8b~ "Income Level"
    )
  ) |> 
  modify_caption(
    "How confident are you that the government considers the public’s opinion when making decisions about the healthcare system"
  )

```

## q41b demographic variabel of district, residence and region

```{r}
q41c_df2<- pvs_data |> 
  select(
    q41c, 
    q4, 
    q4_1, 
    q5
  ) |> 
  mutate(
    across(where(is.character), as.factor)
  )


q41c_df2 |>
  tbl_summary(
    by= q41c,
    missing = "no",
    digits = list(
      q4 ~ c(0, 2),
      q4_1 ~ c(0, 2),
      q5 ~ c(0, 2)
    ),
    label = list(
      q4~ "Region",
      q4_1~ "District",
      q5~ "Residence"
    )
  ) |> 
  modify_caption(
    "How confident are you that the government considers the public’s opinion when making decisions about the healthcare system"
  )
 ```