---
title: "National workshop Analysis Report. MARS Results"
author: "Selemani Ngwira"
date: "2024-11-04"
output: html_document
---

```{r loading packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hold")

pacman::p_load(
  rio,           # to import data
  here,          # to locate files
  tidyverse,     # to clean, handle, and plot the data (includes ggplot2 package)
  sf,            # to manage spatial data using a Simple Feature format
  tmap,          # to produce simple maps, works for both interactive and static maps
  janitor,       # to clean column names
  OpenStreetMap, # to add OSM basemap in ggplot map
  spdep, # spatial statistics
  gganimate, # for animated maps, 
  caTools, 
  gifski
  )

library(summarytools)
library(gtsummary)
library(flextable)
```

## loading data


```{r loading data set}

Mars_data<-read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTUkGOLAkv1p80uzUz0h9uSBCGhdujx8tV1e7Fw5oTjE8NZmh2OXtTM65iuvzONGQ/pub?output=csv")

# cleaning the variable names 

Mars_data1 <- clean_names(Mars_data)


# chaning all the column with character to factor.
Mars_data1<- Mars_data1 %>% 
  mutate(across(where(is.character), as.factor))

```

## Engagement Score

The engagement Section had 5 five questions. The total score under this section is 25. 

```{r Engagement Score, echo=FALSE}

# sub setting engagement variables 
engag_score<-Mars_data %>% 
  select(c(8:12))


# creating freq table
table1<- engag_score %>% 
  tbl_summary()

# converting the gt table to flexable table 
table1<- table1 %>% 
  as_flex_table() %>% 
  autofit()

# save a flextable as a word document
save_as_docx(table1, path = "table1.docx")
  



engag_score_2 <-Mars_data1%>% 
  mutate(
  covid_19_whats_app_chatbot_fun_entertaining_to_use=recode(
    covid_19_whats_app_chatbot_fun_entertaining_to_use, 
"4 Moderately fun and entertaining, would entertain user for some time (5-10 minutes total)"=4, 
"5 Highly entertaining and fun, would stimulate repeat use"=5, 
"2 Mostly boring"=2, 
"3 OK, fun enough to entertain the user for a brief time (< 5 minutes)"=3
  )  
  ) %>% 
  mutate(
  covid_19_whats_app_chatbot_enjoyable_to_use=recode(
    covid_19_whats_app_chatbot_enjoyable_to_use, 
  "5 Very interesting, would engage the user in repeat use" =5, 
  "4 Moderately interesting; would engage the user for some time (5-10 minutes total)"=4, 
"3 OK, neither exciting nor uninteresting; would engage the user for a brief time (< 5 minutes)"=3, 
"2 Mostly uninteresting"=2
  )  
  ) %>% 
  mutate(
covid_19_whats_app_chatbot_provide_retain_all_necessary_preferences_features=recode(
  covid_19_whats_app_chatbot_provide_retain_all_necessary_preferences_features, 
  "4.     Allows numerous options for customisation"=4, 
 "5.     Allows complete tailoring to the individual’s characteristics/preferences retains all settings"=5, 
 "2.     Allows insufficient customisation limiting functions"=2, 
 "3.     Allows basic customisation to function adequately" =3, 
 "1.     Does not allow any customisation or requires setting to be input every time"=1
)
  ) %>% 
  mutate(
    covid_19_whats_app_chatbot_allow_user_input_provide_feedback_and_contain_prompts=recode(
      covid_19_whats_app_chatbot_allow_user_input_provide_feedback_and_contain_prompts, 
  "4.     Offers a variety of interactive features/feedback/user input options"=4, 
  "5.     Very high level of responsiveness through interactive features/feedback/user input options"=5, 
  "3.     Basic interactive features to function adequately"=3, 
  "2.     Insufficient interactivity, or feedback, or user input options, limiting functions"=2,
  "1.     No interactive features and/or no response to user interaction"=1
    )
  ) %>% 
  mutate(
 covid_19_whats_app_chatbot_content_visual_information_language_design=recode(
   covid_19_whats_app_chatbot_content_visual_information_language_design, 
   "5 Perfectly targeted, no issues found"=5, 
   "4 Well-targeted, with negligible issues"=4, 
   "3 Acceptable but not targeted. It may be inappropriate/unclear/confusing"=3, 
   "1 Completely inappropriate/unclear/confusing"=1
 )   
  )


# replacing NA with 0
engag_score_2[is.na(engag_score_2)]<-0

# Calculating the total score of engagement. 

engag_score_2<- engag_score_2 %>% 
  mutate(
    total_score=round(
    covid_19_whats_app_chatbot_fun_entertaining_to_use+
    covid_19_whats_app_chatbot_enjoyable_to_use+
  covid_19_whats_app_chatbot_provide_retain_all_necessary_preferences_features+
 covid_19_whats_app_chatbot_allow_user_input_provide_feedback_and_contain_prompts+
    covid_19_whats_app_chatbot_content_visual_information_language_design  
    ), 
 total_score=round(
   total_score/5
 )
  )
  


mean(engag_score_2$total_score)
sd(engag_score_2$total_score)


mean(engag_score_2$total_score)

max(engag_score_2)/5



```


## Performance Score
The Performance section had 3 Questions. The total score under this section is 15. 
```{r Performance }

Performance_score<- Mars_data %>% 
  select(c(13:15))

# creating a freq table
table3<-Performance_score %>% 
  tbl_summary()

# converting the gt object to flextable 
table3<-table3 %>% 
  as_flex_table() %>% 
  autofit()

# saving the 

save_as_docx(table3, path = "table_3.docx")


unique(Performance_score$the_chatbot_is_interactive_consistent_and_intuitive_across_all_components)

Performance_score_2 <- Performance_score %>% 
  mutate(
 accurately_fastest_of_covid_19_whats_app_chatbot_features_functions_and_components=recode(
 accurately_fastest_of_covid_19_whats_app_chatbot_features_functions_and_components, 
 "5.     Perfect/timely response; no technical bugs found/contains a ‘loading time left’ indicator"=5, 
 "3.     works overall. Some technical problems need fixing/Slow at times"=3, 
 "2.     Some functions work but lagging or contain major technical problems"=2, 
 "4.     Mostly functional with minor/negligible problems"=4
 )   
  ) %>% 
  mutate(
    ease_of_use_of_covid_19_whats_app_chatbot=recode(ease_of_use_of_covid_19_whats_app_chatbot, 
    "5.     Able to use the COVID-19 WhatsApp Chatbot immediately; intuitive; simple"=5,
    "4.     Easy to learn how to use the COVID-19 WhatsApp Chatbot"=4, 
    "3.     Useable after some time/effort"=3
    )
  ) %>% 
  mutate(
  the_chatbot_is_interactive_consistent_and_intuitive_across_all_components=recode(
  the_chatbot_is_interactive_consistent_and_intuitive_across_all_components, 
  "5.     Perfectly consistent and intuitive"=5, 
  "4.     Mostly consistent/intuitive with negligible problems"=4, 
  "2.     Often inconsistent/confusing"=2, 
  "3.     OK with some inconsistencies/confusing elements"=3
  )  
  )


Performance_score_2<- Performance_score_2 %>% 
  mutate(total_score=round(
  accurately_fastest_of_covid_19_whats_app_chatbot_features_functions_and_components+
  ease_of_use_of_covid_19_whats_app_chatbot+ 
  the_chatbot_is_interactive_consistent_and_intuitive_across_all_components
  ))


mean(Performance_score_2$total_score)
sd(Performance_score_2$total_score)

max(perf)

```


## Graphic Score
The Graphic section had 2 Questions. The total score under this section is 10. 
```{r Graphic}

graphic_score<- Mars_data %>% 
  select(c(16:17))

# creating a freq table 

table4 <- graphic_score %>% 
  tbl_summary()

# converting gt object to flextable object
table4<- table4 %>% 
  as_flex_table() %>% 
  autofit()

# saving the table to word document 

save_as_docx(table4, path = "table 4.docx")


unique(graphic_score$chatbot_content_visual_is_appeal_font_color_and_size)


graphic_score_2 <- graphic_score %>% 
  mutate(
  chatbot_graphics_are_of_quality_resolution_for_used_icons_menus_content=recode(
    chatbot_graphics_are_of_quality_resolution_for_used_icons_menus_content, 
 "5.     Very high-quality/resolution graphics and visual design - proportionate, stylistically consistent  throughout"=5, 
 "4.     High-quality/resolution graphics and visual design – mostly proportionate, stylistically consistent"=4, 
 "3.     Moderate-quality graphics and visual design (generally consistent in style)"=3
  )  
  ) %>% 
  mutate(
  chatbot_content_visual_is_appeal_font_color_and_size=recode(
    chatbot_content_visual_is_appeal_font_color_and_size, 
  "4.     High level of visual appeal – seamless graphics – consistent and professionally designed"=4, 
  "5.     As above + very attractive, memorable, stands out; use of colour enhances app features/menus"=5, 
  "3.     Some visual appeal – average, neither pleasant nor unpleasant" =3, 
  "2.     Little visual appeal – poorly designed, bad use of colour/font/Size, visually boring"=2
  
  )  
  )


graphic_score_2<- graphic_score_2 %>% 
  mutate(
    total_score=round(
      chatbot_graphics_are_of_quality_resolution_for_used_icons_menus_content+ chatbot_content_visual_is_appeal_font_color_and_size
    )
  )


# replace NA with Zeros

graphic_score_2[is.na(graphic_score_2)] <- 0

mean(graphic_score_2$total_score)

sd(graphic_score_2$total_score)

table4

```

## Information 

The Information section had 3 Questions. The total score under this section is 15.
```{r information}
information_score<- Mars_data %>% 
  select(c(18:20))

# creating frequency table
table2<-information_score %>% 
  tbl_summary()

# converting gt object to flextable object 
table2<- table2 %>% 
  as_flex_table() %>% 
  autofit()

# save the table in to word document. 

save_as_docx(table2, path = "table 2.docx")



names(information_score)
unique(information_score$covid_19_whats_app_chatbot_scope_comprehensive_and_concise)


information_score_2<-information_score %>% 
  mutate(covid_19_whats_app_chatbot_profile_contain_its_purpose=recode(
    covid_19_whats_app_chatbot_profile_contain_its_purpose, 
    "5. Highly accurate description of the the COVID-19 WhatsApp Chatbot components/functions on the profile."=5, 
    "4. Accurate. the COVID-19 WhatsApp Chatbot profile contains most of the described components/functions"=4, 
    "2. Inaccurate. The profile contains very few of the described components/functions"=2, 
    "3. OK. the COVID-19 WhatsApp Chatbot profile contains some of the described components/ functions"=3
  )) %>% 
  mutate(covid_19_whats_app_chatbot_content_is_correct_well_written_and_relevant=recode(
    covid_19_whats_app_chatbot_content_is_correct_well_written_and_relevant, 
    "4 Relevant/appropriate/coherent/correct"=4, 
    "5 Highly relevant, appropriate, coherent, and correct"=5, 
    "3 Moderately relevant/appropriate/coherent/and appears correct"=3
  )
    
  ) %>% 
  mutate(
    covid_19_whats_app_chatbot_scope_comprehensive_and_concise=recode(
      covid_19_whats_app_chatbot_scope_comprehensive_and_concise, 
   "4 Offers a broad range of information, has some gaps or unnecessary detail; or has no links to more information and resources"=4, 
   "5 Comprehensive and concise; contains links to more information and resources"=5, 
   "3 OK but not comprehensive or concise"=3, 
   "2 Insufficient or possibly overwhelming"=2
    )
  )

# replacing Zero with NA
information_score_2[is.na(information_score_2)]<-0

# calculating information mean score

information_score_2<- information_score_2 %>% 
  mutate(total_socre=round(
   covid_19_whats_app_chatbot_profile_contain_its_purpose+
   covid_19_whats_app_chatbot_content_is_correct_well_written_and_relevant+
   covid_19_whats_app_chatbot_scope_comprehensive_and_concise  
  ))


# mean score 
mean(information_score_2$total_socre)
sd(information_score_2$total_socre)

table2
```

## Quality 
The Quality section had 3 Questions. The total score under this section is 15
```{r Qaulity}
qaulity_score<- Mars_data %>% 
  select(c(21:23))


# creating freq table. 

table5 <- qaulity_score %>% 
  tbl_summary()

# conversting the gt object to flextable object

table5<- table5 %>% 
  as_flex_table() %>% 
  autofit()

# saving the object as word document 

save_as_docx(table5, path = "table5.docx")


unique(qaulity_score$star_rating_of_the_covid_19_whats_app_chatbot)

qaulity_score2<-qaulity_score %>% 
  mutate(
  recommend_covid_19_whats_app_chatbot_to_people_who_might_benefit_from_it=recode(
recommend_covid_19_whats_app_chatbot_to_people_who_might_benefit_from_it, 
"5 Definitely I would recommend this app to everyone"=5, 
"1 Not at all I would not recommend this app to anyone"=1, 
"4 There are many people I would recommend this app to"=4, 
"3 Maybe There are several people whom I would recommend it to"=3, 
"2 There are very few people I would recommend this app to"=2
  ) 
  ) %>% 
  mutate(
  number_of_time_to_use_covid_19_whats_app_chatbot=recode(
  number_of_time_to_use_covid_19_whats_app_chatbot,
  "5 >50"=5,
  "4 10-50"=4, 
  "3 3-10"=3, 
  "1 None"=1
  )  
  ) %>% 
  mutate(
  star_rating_of_the_covid_19_whats_app_chatbot=recode(
  star_rating_of_the_covid_19_whats_app_chatbot, 
  
  "4 ★★★★" 
  =4, 
  "5 ★★★★★ One of the best apps I've used"
  =5, 
  "3 ★★★ Average"
  =3, 
  "1 ★ One of the worst apps I’ve used"=1
  
  )) 

# calculating subjective score 


qaulity_score2<- qaulity_score2 %>% 
  mutate(
    total_score=round(
   recommend_covid_19_whats_app_chatbot_to_people_who_might_benefit_from_it+
    number_of_time_to_use_covid_19_whats_app_chatbot+
    star_rating_of_the_covid_19_whats_app_chatbot 
    )
  )


# replacing NA with Zeros 

qaulity_score2[is.na(qaulity_score2)] <- 0
mean(qaulity_score2$total_score)
sd(qaulity_score2$total_score)

hist(qaulity_score2$total_score)


```


## Knowledge, Attitude and Intentions 
```{r Knowledge Attitude and Intentions}
Knowledge_Atti_Inten<- Mars_data %>% 
  select(c(24:29))


# change the data stractures 

table6 <- Knowledge_Atti_Inten %>% 
  pivot_longer(
    cols = c(1:6)
  ) 
  # group_by(name) %>% 
  # drop_na(value) %>% 
  # count(value) 
  # pivot_wider(
  #   names_from = "value", 
  #   values_from = "n"
  # )


# replacing underscore with spaces
table6$name <-gsub("_", " ", table6$name)


table6
table6<-table6 %>% 
  tbl_summary(by=value, 
              percent = "row")

table6<- table6 %>% 
  as_flex_table() %>% 
  autofit()


save_as_docx(table6, path = "table6.docx")

table6


names(Knowledge_Atti_Inten)



Knowledge_Atti_Inten %>% 
  mutate(
    chatbot_increase_awareness_of_the_importance_of_addressing_covid_19_myths=
      recode(
    chatbot_increase_awareness_of_the_importance_of_addressing_covid_19_myths, 
     "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5
      ), 
    
    whats_app_chatbot_is_likely_to_encourage_the_general_public_to_test_for_covid_19_vaccinated=recode(
  whats_app_chatbot_is_likely_to_encourage_the_general_public_to_test_for_covid_19_vaccinated, 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    ), 

whats_app_chatbot_is_likely_to_increase_knowledge_understanding_of_covid_19=recode(
  whats_app_chatbot_is_likely_to_increase_knowledge_understanding_of_covid_19, 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    ), 



whats_app_chatbot_is_likely_to_change_attitudes_toward_improving_covid_19_response=recode(
whats_app_chatbot_is_likely_to_change_attitudes_toward_improving_covid_19_response, 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    ), 


chatbot_is_likely_to_increase_intentions_motivation_to_get_covid_19_vaccination_test=recode(
chatbot_is_likely_to_increase_intentions_motivation_to_get_covid_19_vaccination_test    , 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    ), 

whats_app_chatbot_is_likely_to_increase_covid_19_related_healthy_behaviours
  =recode(
whats_app_chatbot_is_likely_to_increase_covid_19_related_healthy_behaviours    , 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    )

  )


names(Knowledge_Atti_Inten)
```

# overal MARS score
Calculating the overall mean score of the Mars on the Malawi COVID-19 chatbot

```{r}

Mars_data1<- Mars_data1 %>% mutate(
  covid_19_whats_app_chatbot_fun_entertaining_to_use=recode(
    covid_19_whats_app_chatbot_fun_entertaining_to_use, 
"4 Moderately fun and entertaining, would entertain user for some time (5-10 minutes total)"=4, 
"5 Highly entertaining and fun, would stimulate repeat use"=5, 
"2 Mostly boring"=2, 
"3 OK, fun enough to entertain the user for a brief time (< 5 minutes)"=3
  )  
  ) %>% 
  mutate(
  covid_19_whats_app_chatbot_enjoyable_to_use=recode(
    covid_19_whats_app_chatbot_enjoyable_to_use, 
  "5 Very interesting, would engage the user in repeat use" =5, 
  "4 Moderately interesting; would engage the user for some time (5-10 minutes total)"=4, 
"3 OK, neither exciting nor uninteresting; would engage the user for a brief time (< 5 minutes)"=3, 
"2 Mostly uninteresting"=2
  )  
  ) %>% 
  mutate(
covid_19_whats_app_chatbot_provide_retain_all_necessary_preferences_features=recode(
  covid_19_whats_app_chatbot_provide_retain_all_necessary_preferences_features, 
  "4.     Allows numerous options for customisation"=4, 
 "5.     Allows complete tailoring to the individual’s characteristics/preferences retains all settings"=5, 
 "2.     Allows insufficient customisation limiting functions"=2, 
 "3.     Allows basic customisation to function adequately" =3, 
 "1.     Does not allow any customisation or requires setting to be input every time"=1
)
  ) %>% 
  mutate(
    covid_19_whats_app_chatbot_allow_user_input_provide_feedback_and_contain_prompts=recode(
      covid_19_whats_app_chatbot_allow_user_input_provide_feedback_and_contain_prompts, 
  "4.     Offers a variety of interactive features/feedback/user input options"=4, 
  "5.     Very high level of responsiveness through interactive features/feedback/user input options"=5, 
  "3.     Basic interactive features to function adequately"=3, 
  "2.     Insufficient interactivity, or feedback, or user input options, limiting functions"=2,
  "1.     No interactive features and/or no response to user interaction"=1
    )
  ) %>% 
  mutate(
 covid_19_whats_app_chatbot_content_visual_information_language_design=recode(
   covid_19_whats_app_chatbot_content_visual_information_language_design, 
   "5 Perfectly targeted, no issues found"=5, 
   "4 Well-targeted, with negligible issues"=4, 
   "3 Acceptable but not targeted. It may be inappropriate/unclear/confusing"=3, 
   "1 Completely inappropriate/unclear/confusing"=1
 )   
  ) %>% 
    mutate(
 accurately_fastest_of_covid_19_whats_app_chatbot_features_functions_and_components=recode(
 accurately_fastest_of_covid_19_whats_app_chatbot_features_functions_and_components, 
 "5.     Perfect/timely response; no technical bugs found/contains a ‘loading time left’ indicator"=5, 
 "3.     works overall. Some technical problems need fixing/Slow at times"=3, 
 "2.     Some functions work but lagging or contain major technical problems"=2, 
 "4.     Mostly functional with minor/negligible problems"=4
 )   
  ) %>% 
  mutate(
    ease_of_use_of_covid_19_whats_app_chatbot=recode(ease_of_use_of_covid_19_whats_app_chatbot, 
    "5.     Able to use the COVID-19 WhatsApp Chatbot immediately; intuitive; simple"=5,
    "4.     Easy to learn how to use the COVID-19 WhatsApp Chatbot"=4, 
    "3.     Useable after some time/effort"=3
    )
  ) %>% 
  mutate(
  the_chatbot_is_interactive_consistent_and_intuitive_across_all_components=recode(
  the_chatbot_is_interactive_consistent_and_intuitive_across_all_components, 
  "5.     Perfectly consistent and intuitive"=5, 
  "4.     Mostly consistent/intuitive with negligible problems"=4, 
  "2.     Often inconsistent/confusing"=2, 
  "3.     OK with some inconsistencies/confusing elements"=3
  )  
  ) %>% 
   mutate(
  chatbot_graphics_are_of_quality_resolution_for_used_icons_menus_content=recode(
    chatbot_graphics_are_of_quality_resolution_for_used_icons_menus_content, 
 "5.     Very high-quality/resolution graphics and visual design - proportionate, stylistically consistent  throughout"=5, 
 "4.     High-quality/resolution graphics and visual design – mostly proportionate, stylistically consistent"=4, 
 "3.     Moderate-quality graphics and visual design (generally consistent in style)"=3
  )  
  ) %>% 
  mutate(
  chatbot_content_visual_is_appeal_font_color_and_size=recode(
    chatbot_content_visual_is_appeal_font_color_and_size, 
  "4.     High level of visual appeal – seamless graphics – consistent and professionally designed"=4, 
  "5.     As above + very attractive, memorable, stands out; use of colour enhances app features/menus"=5, 
  "3.     Some visual appeal – average, neither pleasant nor unpleasant" =3, 
  "2.     Little visual appeal – poorly designed, bad use of colour/font/Size, visually boring"=2
  
  )  
  ) %>% 
    mutate(covid_19_whats_app_chatbot_profile_contain_its_purpose=recode(
    covid_19_whats_app_chatbot_profile_contain_its_purpose, 
    "5. Highly accurate description of the the COVID-19 WhatsApp Chatbot components/functions on the profile."=5, 
    "4. Accurate. the COVID-19 WhatsApp Chatbot profile contains most of the described components/functions"=4, 
    "2. Inaccurate. The profile contains very few of the described components/functions"=2, 
    "3. OK. the COVID-19 WhatsApp Chatbot profile contains some of the described components/ functions"=3
  )) %>% 
  mutate(covid_19_whats_app_chatbot_content_is_correct_well_written_and_relevant=recode(
    covid_19_whats_app_chatbot_content_is_correct_well_written_and_relevant, 
    "4 Relevant/appropriate/coherent/correct"=4, 
    "5 Highly relevant, appropriate, coherent, and correct"=5, 
    "3 Moderately relevant/appropriate/coherent/and appears correct"=3
  )
    
  ) %>% 
  mutate(
    covid_19_whats_app_chatbot_scope_comprehensive_and_concise=recode(
      covid_19_whats_app_chatbot_scope_comprehensive_and_concise, 
   "4 Offers a broad range of information, has some gaps or unnecessary detail; or has no links to more information and resources"=4, 
   "5 Comprehensive and concise; contains links to more information and resources"=5, 
   "3 OK but not comprehensive or concise"=3, 
   "2 Insufficient or possibly overwhelming"=2
    )
  ) %>% 
    mutate(
  recommend_covid_19_whats_app_chatbot_to_people_who_might_benefit_from_it=recode(
recommend_covid_19_whats_app_chatbot_to_people_who_might_benefit_from_it, 
"5 Definitely I would recommend this app to everyone"=5, 
"1 Not at all I would not recommend this app to anyone"=1, 
"4 There are many people I would recommend this app to"=4, 
"3 Maybe There are several people whom I would recommend it to"=3, 
"2 There are very few people I would recommend this app to"=2
  ) 
  ) %>% 
  mutate(
  number_of_time_to_use_covid_19_whats_app_chatbot=recode(
  number_of_time_to_use_covid_19_whats_app_chatbot,
  "5 >50"=5,
  "4 10-50"=4, 
  "3 3-10"=3, 
  "1 None"=1
  )  
  ) %>% 
  mutate(
  star_rating_of_the_covid_19_whats_app_chatbot=recode(
  star_rating_of_the_covid_19_whats_app_chatbot, 
  
  "4 ★★★★" 
  =4, 
  "5 ★★★★★ One of the best apps I've used"
  =5, 
  "3 ★★★ Average"
  =3, 
  "1 ★ One of the worst apps I’ve used"=1
  
  )) %>% 
    mutate(
    chatbot_increase_awareness_of_the_importance_of_addressing_covid_19_myths=
      recode(
    chatbot_increase_awareness_of_the_importance_of_addressing_covid_19_myths, 
     "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5
      ), 
    
    whats_app_chatbot_is_likely_to_encourage_the_general_public_to_test_for_covid_19_vaccinated=recode(
  whats_app_chatbot_is_likely_to_encourage_the_general_public_to_test_for_covid_19_vaccinated, 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    ), 

whats_app_chatbot_is_likely_to_increase_knowledge_understanding_of_covid_19=recode(
  whats_app_chatbot_is_likely_to_increase_knowledge_understanding_of_covid_19, 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    ), 



whats_app_chatbot_is_likely_to_change_attitudes_toward_improving_covid_19_response=recode(
whats_app_chatbot_is_likely_to_change_attitudes_toward_improving_covid_19_response, 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    ), 


chatbot_is_likely_to_increase_intentions_motivation_to_get_covid_19_vaccination_test=recode(
chatbot_is_likely_to_increase_intentions_motivation_to_get_covid_19_vaccination_test    , 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    ), 

whats_app_chatbot_is_likely_to_increase_covid_19_related_healthy_behaviours
  =recode(
whats_app_chatbot_is_likely_to_increase_covid_19_related_healthy_behaviours    , 
  
  "2.     Disagree" =2, 
    "3.     Neutral"=3, 
    "4.     Agree"=4, 
    "5.     Strongly Agree"=5, 
  "1.     Strongly disagree"=1
    )

  )

# deselection ID, age_group and technical aspects

Mars_data1<- Mars_data1 %>% 
  select(-c(id, age_group_all_that_apply, technical_aspects_of_the_app_all_that_apply))

# replacing all NA with Zeros
# Replace NA values with 0 in numeric columns
Mars_data1[sapply(Mars_data1, is.numeric)] <- lapply(Mars_data1[sapply(Mars_data1, is.numeric)], function(x) replace(x, is.na(x), 0))






Mars_data1<-Mars_data1 %>% mutate( 
    Quality=round(
   recommend_covid_19_whats_app_chatbot_to_people_who_might_benefit_from_it+
    number_of_time_to_use_covid_19_whats_app_chatbot+
    star_rating_of_the_covid_19_whats_app_chatbot 
    ), 
   Quality=round(
   Quality/3  
   )
  ) %>% 
  mutate(
    Engagement=round(
    covid_19_whats_app_chatbot_fun_entertaining_to_use+
    covid_19_whats_app_chatbot_enjoyable_to_use+
  covid_19_whats_app_chatbot_provide_retain_all_necessary_preferences_features+
 covid_19_whats_app_chatbot_allow_user_input_provide_feedback_and_contain_prompts+
    covid_19_whats_app_chatbot_content_visual_information_language_design  
    ), 
 Engagement=round(
   Engagement/5
 )
  ) %>% 
  mutate(Functionality=round(
  accurately_fastest_of_covid_19_whats_app_chatbot_features_functions_and_components+
  ease_of_use_of_covid_19_whats_app_chatbot+ 
  the_chatbot_is_interactive_consistent_and_intuitive_across_all_components
  ), 
    Functionality=round(
    Functionality/3
  )
  
  ) %>% 
  mutate(
    Aesthetic=round(
      chatbot_graphics_are_of_quality_resolution_for_used_icons_menus_content+ chatbot_content_visual_is_appeal_font_color_and_size
    ), 
   Aesthetic=round(
    Aesthetic/2 
   ) 
  ) %>% 
   mutate(Information=round(
   covid_19_whats_app_chatbot_profile_contain_its_purpose+
   covid_19_whats_app_chatbot_content_is_correct_well_written_and_relevant+
   covid_19_whats_app_chatbot_scope_comprehensive_and_concise  
  ), 
  
    Information=round(
      Information/3
    )
  ) %>% 
  mutate(
   
    `Subjective quality`=round(
    
    chatbot_increase_awareness_of_the_importance_of_addressing_covid_19_myths+
    whats_app_chatbot_is_likely_to_increase_knowledge_understanding_of_covid_19+  whats_app_chatbot_is_likely_to_change_attitudes_toward_improving_covid_19_response+
chatbot_is_likely_to_increase_intentions_motivation_to_get_covid_19_vaccination_test+
  whats_app_chatbot_is_likely_to_encourage_the_general_public_to_test_for_covid_19_vaccinated+
  whats_app_chatbot_is_likely_to_increase_covid_19_related_healthy_behaviours
    ), 

`Subjective quality`=round(
  `Subjective quality`/6
)
  )


```

# restructuring the data for boxplot


```{r}

Mars_data_long <- Mars_data1 %>%
  dplyr::select(Quality, 
                Engagement,
                Functionality, 
                Aesthetic,
                Information, 
                `Subjective quality`, 
                affiliations) %>%
  pivot_longer(
         cols = c(Quality, 
                Engagement,
                Functionality, 
                Aesthetic,
                Information, 
                `Subjective quality`),
    names_to = "Variable",
    values_to = "Score"
  )

# calculating the mean of the score for each variable
tapply( Mars_data_long$Score, Mars_data_long$Variable, mean)

# the overall mean score 
mean(Mars_data_long$Score, na.rm = T)

# the overall sd
sd(Mars_data_long$Score, na.rm = T)


# calculating the mean of the score among the general public and MoH
tapply(
   Mars_data_long$Score,
   Mars_data_long$affiliations,
  mean, na.rm=T)


# calculating the sd of the score among the general public and MoH
tapply(
   Mars_data_long$Score,
   Mars_data_long$affiliations,
   sd, na.rm=T )
 

```


## ploting the boxplot 
```{r}

#Creating the boxplot with mean and median lines
Mars_data_long %>%
  ggplot(aes(x = Variable, y = Score, fill = Variable)) +
  geom_boxplot(alpha = 0.6) + # Boxplots with variable-specific colors
  stat_summary(
    fun = mean,
    geom = "point",
    color = "red",
    size = 3,
    shape = 20
  ) + # Mean as red points
  stat_summary(
    fun = mean,
    geom = "errorbar",
    aes(ymin = ..y.., ymax = ..y..),
    linetype = "dotted",
    color = "red",
    width = 0.75
  ) + # Mean as dotted lines
  stat_summary(
    fun = median,
    geom = "errorbar",
    aes(ymin = ..y.., ymax = ..y..),
    color = "blue",
    size = 1,
    width = 0.75
  ) + # Median as solid blue lines
  scale_fill_brewer(palette = "Set3") + # Color palette for variable-specific colors
   facet_wrap(~affilications, scales = "free_y")+
  theme_minimal() +
  labs(
    title = "Malawi COVID-19 Chatbot scores",
    x = "MARS Dimension ",
    y = "Mean Scores", 
    caption = "Mean(Red dotted line), Median(Blue solid line)"
  )+
   guides(fill = "none")+
  theme(
    axis.text.x = element_text(
      angle = 35, colour = "black", size = 12
    ), 
    axis.text.y = element_text( colour = "black", size = 12
    )
  )


# 
# ggsave(plot = plots_score, "Plot_sscores.png", bg = "white", dpi = 300)
# 
# plots_score


```

# t.test 
The t.test is run to test the  difference in mean score between MoH and General Public

```{r}

t_test<-Mars_data_long %>%
  group_by(affiliations, Variable) %>% 
  summarise(Score=mean(Score)) %>% 
    pivot_wider(
         names_from = affiliations,
         values_from= Score
    )

# checking difference in variance 
var.test( t_test$Moh , t_test$`general public` )
 
# runing the t.test 
t.test( t_test$Moh , t_test$`general public`)


```

# Quality test for difference in mean score between the two groups

```{r}


 quality_test<- Mars_data_long %>% 
   mutate(ID = row_number()) %>% 
  pivot_wider(
          names_from = affiliations, 
    values_from = Score
  ) %>% 
  select(-ID) %>% 
  filter(Variable=="Quality") %>% 
  print(n=Inf)
  
    

  
# Replace NA values with 0 in numeric columns
quality_test[sapply(quality_test, is.numeric)] <- lapply(quality_test[sapply(quality_test, is.numeric)], function(x) replace(x, is.na(x), 0)) 



my_fun(data = quality_test,
  "general public" , "Moh")




```


# Engagement test for difference in mean score between the two groups


```{r}

 Functionality_test<- Mars_data_long %>% 
   mutate(ID = row_number()) %>% 
  pivot_wider(
          names_from = affiliations, 
    values_from = Score
  ) %>% 
  select(-ID) %>% 
  filter(Variable=="Functionality") %>% 
  print(n=Inf)
  
    

  
# Replace NA values with 0 in numeric columns
Functionality_test[sapply(Functionality_test, is.numeric)] <- lapply(Functionality_test[sapply(Functionality_test, is.numeric)], function(x) replace(x, is.na(x), 0)) 



my_fun(data = Functionality_test,
  "general public" , "Moh")



```

# Aesthetic test for difference in mean score between the two groups


```{r}


 Aesthetic_test<- Mars_data_long %>% 
   mutate(ID = row_number()) %>% 
  pivot_wider(
          names_from = affiliations, 
    values_from = Score
  ) %>% 
  select(-ID) %>% 
  filter(Variable=="Aesthetic") %>% 
  print(n=Inf)
  
    

  
# Replace NA values with 0 in numeric columns
Aesthetic_test[sapply(Aesthetic_test, is.numeric)] <- lapply(Aesthetic_test[sapply(Aesthetic_test, is.numeric)], function(x) replace(x, is.na(x), 0)) 



my_fun(data = Aesthetic_test,
  "Moh" , "general public")

```


# Information test for difference in mean score between the two groups


```{r}

Information_test<- Mars_data_long %>% 
   mutate(ID = row_number()) %>% 
  pivot_wider(
          names_from = affiliations, 
    values_from = Score
  ) %>% 
  select(-ID) %>% 
  filter(Variable=="Information") %>% 
  print(n=Inf)
  
    

  
# Replace NA values with 0 in numeric columns
Information_test[sapply(Information_test, is.numeric)] <- lapply(Information_test[sapply(Information_test, is.numeric)], function(x) replace(x, is.na(x), 0)) 



my_fun(data = Information_test,
  "Moh" , "general public")



```

# Subjective quality test for difference in mean score between the two groups


```{r}



Subjective_quality_test<- Mars_data_long %>% 
   mutate(ID = row_number()) %>% 
  pivot_wider(
          names_from = affiliations, 
    values_from = Score
  ) %>% 
  select(-ID) %>% 
  filter(Variable=="Subjective quality") %>% 
  print(n=Inf)
  
    

  
# Replace NA values with 0 in numeric columns
Subjective_quality_test[sapply(Subjective_quality_test, is.numeric)] <- lapply(Subjective_quality_test[sapply(Subjective_quality_test, is.numeric)], function(x) replace(x, is.na(x), 0)) 



my_fun(data = Subjective_quality_test,
 "Moh" , "general public")



```


# the fifference between MoH and General Public in the mean score of the Malawi COVID-19 chatbot


```{r}

 Mean_score_table<- Mars_data_long %>% 
  group_by(Variable) %>% 
  summarise(
  `mean score MoH`=mean(Score[affiliations=="Moh"]),
  `mean score general public`=mean(Score[affiliations=="general public"])
  )

Mean_score_table <- Mean_score_table %>% 
  as_flextable() %>% 
  autofit()

Mean_score_table

save_as_docx(
  Mean_score_table, 
  path = here("output/mean score.docx"))




```





