---
title: "Sampling"
author: "Selemani Ngwira"
date: "2024-08-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# loading packages 

library(rio)
library(tidyverse)
library(janitor)

```

## Loading Data


```{r cars}

MHFR_facility<-import("MHFR_Facilities.xlsx")

# cleaning the variable names

MHFR_facility<-clean_names(MHFR_facility)

attributes(MHFR_facility)$names

unique(MHFR_facility$status)


```

## Sampling 

10 districts of Blantyre, Likoma, Mzimba-South, Mzimba North, Lilongwe, Neno, Zomba, Mwanza, Ntchisi, and Rumphi were stratified using the mean AR of 4.12 per 1000 population 


```{r pressure, echo=FALSE}

# check the name of the district values 

unique(MHFR_facility$district)

sampled_districts<-MHFR_facility %>% 
  filter(district=="Blantyre"|district=="Likoma"|district=="Lilongwe"| district=="Mzimba"|
           district=="Neno"| district=="Zomba"| district=="Mwanza"| district=="Ntchisi"|
           district=="Rumphi"| district=="Mzuzu Central") %>% 
  filter(status=="Functional")

# checking the names of the district in the sampled district data set
unique(sampled_districts$district)

unique(sampled_districts$ownership)


sampled_districts %>% 
  count(common_name) %>% 
  summarise(n=sum(n))

sampled_districts %>% 
  filter(ownership=="Government") %>% 
  count(common_name) %>% 
  summarise(n=sum(n))


#  Blantyre sampling 

Blantyre_hf<-sampled_districts %>% 
  filter(district=="Blantyre") %>% 
   filter(ownership=="Government")

 ## sample health facilities for Blantyre District. the code will be run once 

 sample(Blantyre_hf$name, 15, replace = F)
 
 # using the code above Mpemba Health facility was picked. 
 
# Likoma Sampling 
 
Likoma_hf<-sampled_districts %>% 
  filter(district=="Likoma") %>% 
   filter(ownership=="Government")

  ## sampling hf for likoma district. the code is run once. 

sample(Likoma_hf$common_name, 1, replace = T)
 
## using the code above St.Marys was picked. 

# Lilongwe Sampling 

Lilongwe_hf<-sampled_districts %>% 
  filter(district=="Lilongwe") %>% 
   filter(ownership=="Government")

## Sampling a hf in lilongwe district . the code is run once. 

sample(Lilongwe_hf$name, 6, replace = F)

## using the code above Chinsapo Clinic was picked.


# Mzimba South

Mzimba_S_hf<-sampled_districts %>% 
    filter(district=="Mzimba") %>% 
   filter(ownership=="Government")

## Sampling hfs for Mzimba North and South. this code was run 4 times. 

sample(Mzimba_S_hf$name, 8, replace = F)
## Zolozolo and Madede were pick for Mzimba North and Mzimba South respectively


# Neno Sampling 

Neno_hf<-sampled_districts %>% 
   filter(district=="Neno") %>% 
   filter(ownership=="Government")

## sampling hf for Neno district. the Code is run once. 

sample(Neno_hf$name, 5, replace = F) 
## using the code above Ligowe was picked. 



# Zomba Sampling 

Zomba_hf<-sampled_districts %>% 
   filter(district=="Zomba") %>% 
   filter(ownership=="Government")

## Sampling hf for Zomba district. the code is run once

sample(Zomba_hf$name, 3, replace = F)

## using the code above Likangala was picked. 


# Mwanza Sampling. 

Mwanza_hf<-sampled_districts %>% 
   filter(district=="Mwanza") %>% 
   filter(ownership=="Government")

## Sampling hf for Mwanza district. the code is run once. 

sample(Mwanza_hf$name, 3, replace = F)

## using the code above Mwanza Border post was picked 


# Ntchisi Sampling 

Ntchisi_hf<-sampled_districts %>% 
   filter(district=="Ntchisi") %>% 
   filter(ownership=="Government")


## sampling hf for Ntchisi district. code is run once 

sample(Ntchisi_hf$name, 3, replace = F)

## using the code above Khuwi Health Centre was picked. 


# Rumphi Sampling 
Rumphi_hf<-sampled_districts %>% 
   filter(district=="Rumphi") %>% 
   filter(ownership=="Government")

## sampling hf for Rumphi District. the code is run once. 

sample(Rumphi_hf$name, 3, replace = T)

## using the code above Luviri Health Post was picked. 



```


The CBO's came from the same district that were stratified. 

# Sampling of CBOs
## Loading Data for CBO
In this sampling process, the study is using the CBO database obtain from Mzuni
the list of CBOs is from the ten districts that were selected. 
```{r}
# importing data set of CBOs
CBO_datebase<-import("List_of_CBOs.xlsx")

# Cleaning the varibale of CBOs
CBO_datebase<-clean_names(CBO_datebase)


unique(CBO_datebase$district)

```


## Sampling of CBOs

```{r}

# Blantyre sampling CBO
Blantyre_cbo<-CBO_datebase %>% 
  filter(district=="Blantyre")


sample(Blantyre_cbo$name_of_cbo, 2, replace = T)
# using the code above  "THANDIWE ORPHAN CARE" "JAF FOUNDATION" were picked
 

# Sampling for Likoma

Likoma_cbo<-CBO_datebase %>% 
  filter(district=="Likoma")

sample(Likoma_cbo$name_of_cbo, 2, replace = T)

# using the code above CHITEKO CBO"     "TIGWILIZANE CBO" were picked

# sampling for Mzimba North
Mzuzu_cbo<-CBO_datebase %>% 
  filter(district=="Mzuzu City")

sample(Mzuzu_cbo$name_of_cbo, 2, replace = T)

# using the code above VITUMBIKO CBO" "CHIDESO CBO" were picked. 


View(Mzuzu_cbo)

# Lilongwe 

Lilongwe_cbo<-CBO_datebase %>% 
  filter(district=="Lilongwe")

sample(Lilongwe_cbo$name_of_cbo, 2, replace = T)

# using the above code "ST PETERS YOUTH" and RESTORED HOPE FOR BETTER COMMUNITY



# sampling for Mzimba South
Mzimba_s_cbo<-CBO_datebase %>% 
  filter(district=="Mzimba South")

sample(Mzimba_s_cbo$name_of_cbo, 2, replace = T)

# using the code above CHIHADO CBO"  "LIZIWAZI CBO" were picked. 

# Sampling for Neno 

Neno_cbo<-CBO_datebase %>% 
  filter(district=="Neno")

sample(Neno_cbo$name_of_cbo, 2, replace = T)

# using the code above "MIRACLE CBO" "LIGOWE CBO" were picked. 


# Sampling for Zomba

Zomba_cbo<-CBO_datebase %>% 
  filter(district=="Zomba")

sample(Zomba_cbo$name_of_cbo, 2, replace = T)

# using the above code "AIYDO CBO" and "ADAMS ISLAMIC CENTRE" were picked


# Sampling Mwanza 

Mwanza_cbo<-CBO_datebase %>% 
  filter(district=="Mwanza")

sample(Mwanza_cbo$name_of_cbo, 2, replace = T)

# using the above code  MANKHWALA CBO" "KADAZI CBO" were picked. 

# Sampling for Rumphi 

Rumphi_cbo<-CBO_datebase %>% 
  filter(district=="Rumphi")

sample(Rumphi_cbo$name_of_cbo, 2, replace = T) # this code was run twince because the first produce the one CBO 

# using the code above LUSEHAPE" and "MKOBEKA WOMEN CIRCLE were picked

# sampling for Ntchisi

Ntchisi_cbo<-CBO_datebase %>% 
  filter(district=="Ntchisi")

# in there were two CBO registed in Mzuni CBO database hence we picke all of them


```


# checking for Mzimba North


```{r}

Mzimba_North<-import("Mzimba North_list.xls")

sample(Mzimba_North$name, 4, replace = F)
  
```

# calculating the power of the study 

```{r}
pwr

```

