---
title: "old code"
author: "Selemani Ngwira"
date: "2024-12-16"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)


# loading packages, first load the pacman package using a logic code

if(!require(pacman)) install.packages("pacman")
pacman:: p_load(
  tidyverse, rio, here,
  janitor)


```

---
title: "Cholera Study Analysis"
author: "Selemani Ngwira"
date: "2025-01-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


if(!require(pacman)) install.packages("pacman")

p_load(
  tidyverse,
  here,
  summarytools,
  janitor,
  sf, 
  tmap,
  OpenStreetMap,
  flextable,
  rio, 
  gtsummary, 
  epikit, 
  pwr
)



pwr.p.test(h = ES.h(0.3764, 0.5),
                           n = 797,
                           sig.level = 0.05,
                           alternative = "two.sided")

```

# loading data


```{r cars}


# importing the data 
cholera_data<- import( here("data/cholera_data_.csv")) %>%
                clean_names() %>% 
  mutate(district=recode(
      district, 
      "Blantyre_City"="Blantyre"
    )) %>% 
   mutate(residence = case_when(
    district %in% c("Lilongwe", "Blantyre", "Dedza", "Bakala") ~ "in_land",
    TRUE ~ "lake_share" ))

# changing the data.frame into tibble object for easy handling 
cholera_data<- tibble(cholera_data)



# filtering out those less than 18 years 
cholera_data<-cholera_data %>% 
  filter(age_group!="<18")


ta_shapefile<-st_read(
  here("data/MWI_adm1.shp")
) %>% 
  select(
   NAME_1,
    ID_0,
    ID_1) %>% 
  dplyr::rename(
    "District"= NAME_1
  )








```

# Social and behavioral factors that influence current water treatment practices

## Source of Water for Daily use by District   


```{r pressure, echo=FALSE}







```


## Awareness of the Health Risk Associated with drinking untreated Water by Sex, Age-Group, Level of Education,  and District 

```{r}

awareness_of_heathRisk<-cholera_data %>% 
                 select(
                   sex, 
                   age_group, 
                   level_education, 
                   district,
                   residence,
                   zone,
                   health_risk_associated_with_drinking_untreated_water
                 )


table2<-awareness_of_heathRisk %>% 
          select(-district , -zone, -residence) %>% 
            tbl_summary(health_risk_associated_with_drinking_untreated_water,
            percent = "row",
            digits = list(
              sex ~ c(0, 2),
              age_group ~ c(0, 2),
              level_education ~ c(0, 2)
            ))



table2 <- table2 %>% 
         as_flex_table()


save_as_docx(table2, path = here("output/table2.docx"))




sum(str_detect(cholera_data$ta, "TA"))


# tbale of the Zone and District 


table3<-awareness_of_heathRisk %>% 
    mutate(district=recode(
      district, 
      "Blantyre_City"="Blantyre"
    )) %>% 
          select(district ,  zone, residence, health_risk_associated_with_drinking_untreated_water) %>% 
            tbl_summary(health_risk_associated_with_drinking_untreated_water,
            percent = "row",
            digits = list(
              district~ c(0, 2),
              zone ~ c(0, 2), 
              residence~ c(0,2)
            ))


table3 <- table3 %>% 
         as_flex_table()


save_as_docx(table3, path = here("output/table3.docx"))



```



## 2.3. 0 Main sources of drinking water during the dry season by District/ Township 

```{r}
drinking_dry<-cholera_data %>% 
  select(district, 
         zone, 
         main_source_of_drinking_water_dry_season)


drinking_dry<- drinking_dry %>% 
  group_by( district, 
           main_source_of_drinking_water_dry_season) %>%
  count(main_source_of_drinking_water_dry_season) %>%
    pivot_wider(
    names_from = main_source_of_drinking_water_dry_season, 
    values_from = n
  )

# replacing NA with Zero 
drinking_dry[is.na(drinking_dry)]<-0


table4<- drinking_dry %>% 
  rowwise() %>% 
  mutate(total= sum(across(where(is.numeric))), 
         
         community_standpipe=round(community_standpipe/total*100, 2), 
         borehole_1=round(borehole_1/total*100, 2 ), 
         piped_into_dwelling= round(piped_into_dwelling/total*100, 2), 
         piped_into_yard_plot= round(piped_into_yard_plot/total*100, 2), 
         protected_well_1=round(protected_well_1/total*100, 2), 
         unprotected_well_1=round(unprotected_well_1/total*100, 2), 
         other_drinking_source=round(other_drinking_source/total*100, 2), 
         river_stream=round(river_stream/total*100, 2), 
         spring_1=round(spring_1/total*100, 2), 
         dam=round(dam/total/100, 2), 
         bottled_water=round(bottled_water/total*100, 2), 
         tanker_truck_bower=round(tanker_truck_bower/total*100, 2), 
         lake=round(lake/total*100, 2)
         
         )


   table4<-table4 %>%
  rename_with(~ str_replace_all(., "_", " "))




table4<- table4 %>% 
  as_flextable()


save_as_docx(table4, path = here("output/table4.docx"))



drinking_dry_zone<-cholera_data %>% 
  select(zone, 
         main_source_of_drinking_water_dry_season)

drinking_dry_zone<- drinking_dry_zone%>% 
  group_by( zone, 
           main_source_of_drinking_water_dry_season) %>%
  count(main_source_of_drinking_water_dry_season) %>%
    pivot_wider(
    names_from = main_source_of_drinking_water_dry_season, 
    values_from = n
  )


# replacing NA with Zero 
drinking_dry_zone[is.na(drinking_dry_zone)]<-0

    table5<- drinking_dry_zone %>% 
      rowwise() %>% 
  mutate(total= sum(across(where(is.numeric))), 
         
         community_standpipe=round(community_standpipe/total*100, 2), 
         borehole_1=round(borehole_1/total*100, 2 ), 
         piped_into_dwelling= round(piped_into_dwelling/total*100, 2), 
         piped_into_yard_plot= round(piped_into_yard_plot/total*100, 2), 
         protected_well_1=round(protected_well_1/total*100, 2), 
         unprotected_well_1=round(unprotected_well_1/total*100, 2), 
         other_drinking_source=round(other_drinking_source/total*100, 2), 
         river_stream=round(river_stream/total*100, 2), 
         spring_1=round(spring_1/total*100, 2), 
         dam=round(dam/total/100, 2), 
         bottled_water=round(bottled_water/total*100, 2), 
         tanker_truck_bower=round(tanker_truck_bower/total*100, 2), 
         lake=round(lake/total*100, 2)
         
         )
    
    
    
    table5<-table5 %>%
  rename_with(~ str_replace_all(., "_", " "))
    

    
table5<- table5 %>% 
  as_flextable()


save_as_docx(table5, path = here("output/table5.docx"))


```


## 2.4. 0 Main sources of drinking water during the wet season by District

```{r}

wet_drink_district <- cholera_data %>% 
                      select(district, 
                             main_source_of_drinking_water_wet_season)


wet_drink_district<- wet_drink_district %>% 
  group_by( district, 
           main_source_of_drinking_water_wet_season) %>%
  count(main_source_of_drinking_water_wet_season) %>%
    pivot_wider(
    names_from = main_source_of_drinking_water_wet_season, 
    values_from = n
  )




# replacing NA with Zero 
wet_drink_district[is.na(wet_drink_district)]<-0


table6<- wet_drink_district %>% 
  rowwise() %>% 
  mutate(total= sum(across(where(is.numeric))), 
         
         community_standpipe=round(community_standpipe/total*100, 2), 
         borehole_1=round(borehole_1/total*100, 2 ), 
         piped_into_dwelling= round(piped_into_dwelling/total*100, 2), 
         piped_into_yard_plot= round(piped_into_yard_plot/total*100, 2), 
         protected_well_1=round(protected_well_1/total*100, 2), 
         unprotected_well_1=round(unprotected_well_1/total*100, 2), 
         other_drinking_source=round(other_drinking_source/total*100, 2), 
         river_stream=round(river_stream/total*100, 2), 
         spring_1=round(spring_1/total*100, 2), 
         dam=round(dam/total/100, 2), 
         bottled_water=round(bottled_water/total*100, 2), 
         tanker_truck_bower=round(tanker_truck_bower/total*100, 2), 
         lake=round(lake/total*100, 2)
         
         )


   table6<-table6 %>%
  rename_with(~ str_replace_all(., "_", " "))
   
       
table6<- table6 %>% 
  as_flextable()


save_as_docx(table6, path = here("output/table6.docx"))







# by Zone 


wet_drink_zone <- cholera_data %>% 
                      select(zone, 
                             main_source_of_drinking_water_wet_season)


wet_drink_zone<- wet_drink_zone %>% 
  group_by( zone, 
           main_source_of_drinking_water_wet_season) %>%
  count(main_source_of_drinking_water_wet_season) %>%
    pivot_wider(
    names_from = main_source_of_drinking_water_wet_season, 
    values_from = n
  )




# replacing NA with Zero 
wet_drink_zone[is.na(wet_drink_zone)]<-0


table7<- wet_drink_zone%>% 
  rowwise() %>% 
  mutate(total= sum(across(where(is.numeric))), 
         
         community_standpipe=round(community_standpipe/total*100, 2), 
         borehole_1=round(borehole_1/total*100, 2 ), 
         piped_into_dwelling= round(piped_into_dwelling/total*100, 2), 
         piped_into_yard_plot= round(piped_into_yard_plot/total*100, 2), 
         protected_well_1=round(protected_well_1/total*100, 2), 
         unprotected_well_1=round(unprotected_well_1/total*100, 2), 
         other_drinking_source=round(other_drinking_source/total*100, 2), 
         river_stream=round(river_stream/total*100, 2), 
         spring_1=round(spring_1/total*100, 2), 
         dam=round(dam/total/100, 2), 
         bottled_water=round(bottled_water/total*100, 2), 
         tanker_truck_bower=round(tanker_truck_bower/total*100, 2), 
         lake=round(lake/total*100, 2)
         
         )


   table7<-table7 %>%
  rename_with(~ str_replace_all(., "_", " "))
   
       
table7<- table7 %>% 
  as_flextable()


save_as_docx(table7, path = here("output/table7.docx"))

```

## 2.5.1 Water Treatment at Household by Sex, Level of Education, Religion

```{r}

Water_treat<-cholera_data %>% 
         select(sex, 
                age_group, 
                level_education, 
                religion, 
                treat_drinking_water)


table8<- Water_treat %>% 
  tbl_summary(treat_drinking_water, 
              percent = "row", 
              digits = list(
                sex~ c(0, 2), 
                age_group~c(0,2), 
                level_education~ c(0,2), 
                religion~c(0,2)
              ))

table8<- table8 %>% 
  as_flex_table()


save_as_docx(table8, path = here("output/table8.docx"))


```


## 2.5.2 Water Treatment at Household by District 

```{r}
 


Water_treat_district_zone<-cholera_data %>% 
         select(district, 
                zone, 
                treat_drinking_water)


table9<- Water_treat_district_zone%>% 
  tbl_summary(treat_drinking_water, 
              percent = "row", 
              digits = list(
                district~ c(0, 2), 
                zone~c(0,2)
                
              ))

table9<- table9 %>% 
  as_flex_table()


save_as_docx(table9, path = here("output/table9.docx"))

```


## 2.5.3 if yes, Methods of water treatment by District

```{r, fig.height=7, fig.width=14}
methods_water <- cholera_data %>% 
               select(
                 #sex,
                  # age_group, 
                  # level_education, 
                  religion, 
                 c(34:41)
               )


religion_table<- methods_water %>% 
  pivot_longer(
    cols = (2:9)
  ) %>% 
  drop_na(value) %>% 
  group_by(
    # sex, 
     # age_group, 
    # level_education, 
     religion, 
    name) %>% 
  summarise(value=sum(value)) %>% 
  pivot_wider(
    names_from = name, 
  values_from = value, 
  ) %>% 
  group_by(
    religion
  ) %>% 
  rowwise() %>% 
  mutate(total=sum(across(where(is.numeric))))


sex_table<- sex_table %>% 
  rename(
    "variable"=sex
  )

age_group_table<- age_group_table %>% 
  rename(
    "variable"=age_group
  )


education_table<- education_table %>% 
  rename(
    "variable"=level_education
  )


religion_table<- religion_table %>% 
  rename(
    "variable"=religion
  )


# Combine all tables into one
table10 <- bind_rows(sex_table,
                     age_group_table,
                     education_table,
                     religion_table)



table10<- table10 %>% 
  mutate(
 method_of_water_treatment_boiling= round(method_of_water_treatment_boiling/total*100, 2) ,         
 method_of_water_treatment_ceramic_filter= round(method_of_water_treatment_ceramic_filter/total*100, 2),   
 method_of_water_treatment_filter_with_cloth= round(method_of_water_treatment_filter_with_cloth/total*100, 2),
 method_of_water_treatment_others_methods=round(method_of_water_treatment_others_methods/total*100, 2),    
 method_of_water_treatment_solar_disinfection=round(method_of_water_treatment_solar_disinfection/total*100, 2), 
 method_of_water_treatment_stand_settle=round(method_of_water_treatment_stand_settle/total*100, 2),     
 method_of_water_treatment_use_chlorine= round(method_of_water_treatment_use_chlorine/total*100, 2),
 method_of_water_treatment_use_water_from_tap=round(method_of_water_treatment_use_water_from_tap/total*100, 2) 
    )


table10<- table10 %>%
  rename_with(~ str_replace_all(., "method_of_water_treatment_", " "))


table10<- table10 %>%
  rename_with(~ str_replace_all(., "_", " "))


table10<- table10 %>% 
  as_flextable()


save_as_docx(table10, path = here("output/table10.docx"))
```


```{r}

methods_water_district <- cholera_data %>% 
               select(
                 district, 
                 c(34:41)
               )



tabel11<- methods_water_district %>% 
  pivot_longer(
    cols = (2:9)
  ) %>% 
  drop_na(value) %>% 
  group_by(
    district, 
    name) %>% 
  summarise(value=sum(value)) %>% 
  pivot_wider(
    names_from = name, 
  values_from = value, 
  ) %>% 
  group_by(
    district
  ) %>% 
  rowwise() %>% 
  mutate(total=sum(across(where(is.numeric))))



tabel11<- tabel11 %>% 
mutate(
 method_of_water_treatment_boiling= round(method_of_water_treatment_boiling/total*100, 2) ,         
 method_of_water_treatment_ceramic_filter= round(method_of_water_treatment_ceramic_filter/total*100, 2),   
 method_of_water_treatment_filter_with_cloth= round(method_of_water_treatment_filter_with_cloth/total*100, 2),
 method_of_water_treatment_others_methods=round(method_of_water_treatment_others_methods/total*100, 2),    
 method_of_water_treatment_solar_disinfection=round(method_of_water_treatment_solar_disinfection/total*100, 2), 
 method_of_water_treatment_stand_settle=round(method_of_water_treatment_stand_settle/total*100, 2),     
 method_of_water_treatment_use_chlorine= round(method_of_water_treatment_use_chlorine/total*100, 2),
 method_of_water_treatment_use_water_from_tap=round(method_of_water_treatment_use_water_from_tap/total*100, 2) 
    )




tabel11<- tabel11 %>%
  rename_with(~ str_replace_all(., "method_of_water_treatment_", " "))


tabel11<- tabel11 %>%
  rename_with(~ str_replace_all(., "_", " "))


tabel11<- tabel11%>% 
  as_flextable()


save_as_docx(tabel11, path = here("output/table11.docx"))

```




##2.5.4 Properly chlorination process by district.


```{r}
properly_chro_district <- cholera_data %>% 
            select(district, 
                   chlorination_process_done_correctly)


table12<- properly_chro_district %>% 
  tbl_summary(chlorination_process_done_correctly, 
              percent = "row", 
              digits = list(
                district~c(0,2)
              ))


table12<- table12 %>% 
  as_flex_table()


save_as_docx(table12, path = here("output/table12.docx"))




## by Sex, Age and Education 


properly_chro_demo<- cholera_data %>% 
            select(sex,
                   age_group, 
                   level_education, 
                   religion,
                   chlorination_process_done_correctly)


table13<- properly_chro_demo %>% 
  tbl_summary(chlorination_process_done_correctly, 
              percent = "row", 
              digits = list(
              sex~c(0,2), 
                 age_group~c(0,2), 
                 level_education~c(0,2), 
                 religion~c(0,2)
              ))


table13<- table13 %>% 
  as_flex_table()


save_as_docx(table13, path = here("output/table13.docx"))


```

## 2.5. 5 Frequency of water treatment by Sex, Level of Education, Religion 

```{r}
freq_water_treatment <- cholera_data %>% 
                        select(
                          sex, 
                          age_group, 
                          level_education, 
                          religion, 
                          often_treat_water
                        )



table14<- freq_water_treatment %>% 
  tbl_summary(often_treat_water, 
              digits = list(
                sex~c(0,2), 
                age_group~c(0,2), 
                level_education~c(0,2), 
                religion~c(0,2)
              ))


table14<- table14 %>% 
  as_flex_table()


save_as_docx(table14, path = here("output/table14.docx"))



freq_water_treatment_district <- cholera_data %>% 
                                select(
                                  district,
                                  zone,
                                  often_treat_water
                                )


table15<- freq_water_treatment_district %>% 
          tbl_summary(often_treat_water, 
                      digits = list(
                        district~c(0,2), 
                        zone~c(0,2)
                      ))


table15<- table15 %>% 
  as_flex_table()


save_as_docx(table15, path = here("output/table15.docx"))



```

## 2. 5.6 Access to water treatment product by district 

```{r}

Access_to_water_treatment_pt<-cholera_data %>% 
            select(district, 
                   residence, 
                   difficulties_accessing_water_treatment_products)


Access_to_water_treatment_pt %>% 
    tbl_summary(difficulties_accessing_water_treatment_products,
                percent = "row",
                digits = list(
                  district~c(0,2), 
                  residence~c(0,2)
                ))





```

## 2. 6.0 Knowledge of cholera calendar year.  By Sex, Level of Education, Religion 

```{r}

pwr(h=0.3764, )


```


## 2. 7. 0 Knowledge of the potential Cause of Cholera.

```{r}





 
```

## 2.8. 0 Knowledge of the Prevention Measures of cholera by Sex, Level of Education and Religious Belief.  


```{r}





```

## 2.8. 0 Knowledge of the Prevention Measures of cholera by District 
```{r}





```


## 2. 9.0 Current local measures or campaigns in place to prevent cholera outbreaks by Districts
```{r}




```

# Social and cultural behavior determinants of vaccine uptake 


## 3.1. 0 Aware of Cholera Vaccine by  Age- Group, Sex Level of Education, and 3.1. 1 Aware of Cholera Vaccine by  District and Zone  ?? whcih variable is this? ignore the code below




```{r}

table3.1.0 <- cholera_data |> 
            select(ocv_prevent_cholera,age_group,sex,level_education) %>% 
            tbl_summary(ocv_prevent_cholera,
            percent = "row",
            digits = list(
              sex ~ c(0, 2),
              age_group ~ c(0, 2),
              level_education ~ c(0, 2)
            ))


 
table3.1.0 <-  table3.1.0 %>% 
         as_flex_table()


save_as_docx( table3.1.0, path = here("output/table3_1_0.docx"))


table3.1.1 <- cholera_data |> 
            select(ocv_prevent_cholera,district,zone) %>% 
            tbl_summary(ocv_prevent_cholera,
            percent = "row",
            digits = list(
              district~ c(0, 2),
              zone ~ c(0, 2)
            ))


 
table3.1.1 <-  table3.1.1 %>% 
         as_flex_table()


save_as_docx( table3.1.1, path = here("output/table3_1_1.docx"))


```

## 3.2.0  Believe Cholera Vaccine Prevent Cholera by Sex, Level of Education 

```{r}
table3.2.0 <- cholera_data |> 
            select(ocv_prevent_cholera,age_group,sex,level_education) %>% 
            tbl_summary(ocv_prevent_cholera,
            percent = "row",
            digits = list(
              sex ~ c(0, 2),
              age_group ~ c(0, 2),
              level_education ~ c(0, 2)
            ))


 
table3.2.0 <-  table3.2.0 %>% 
         as_flex_table()


save_as_docx( table3.2.0, path = here("output/table3_2_0.docx"))


```

## 3.2.1  Believe Cholera Vaccine Prevent District and Zone 

```{r}

table3.2.1 <- cholera_data |> 
            select(ocv_prevent_cholera,district,zone) %>% 
            tbl_summary(ocv_prevent_cholera,
            percent = "row",
            digits = list(
              district~ c(0, 2),
              zone ~ c(0, 2)
            ))


 
table3.2.1 <-  table3.2.1 %>% 
         as_flex_table()


save_as_docx( table3.2.1, path = here("output/table3_2_1.docx"))

```

##3.3. 0 Information about Cholera Vaccine  by Sex, Age Group,  Education, Religion 

```{r}





```



## 3.3. 1 Information about Cholera Vaccine  by  District and Zone 

```{r}
table3.2.1 <- cholera_data |> 
            select(ocv_prevent_cholera,district,zone) %>% 
            tbl_summary(ocv_prevent_cholera,
            percent = "row",
            digits = list(
              district~ c(0, 2),
              zone ~ c(0, 2)
            ))


 
table3.2.1 <-  table3.2.1 %>% 
         as_flex_table()


save_as_docx( table3.2.1, path = here("output/table3_2_1.docx"))


```



## 3. 4. 0 Safe of Cholera Vaccine by Sex Age Group Education and Religion 

```{r}

table3.4.0 <- cholera_data %>%
  select(sex, age_group, level_education, religion, safe_vaccine) %>%
  tbl_summary(
    by = safe_vaccine,
    statistic = list(
      sex ~ "{n} ({p}%)",
      age_group ~ "{n} ({p}%)",
      level_education ~ "{n} ({p}%)",
      religion ~ "{n} ({p}%)"
    ),
    digits = list(
      sex ~ c(0, 2),
      age_group ~ c(0, 2),
      level_education ~ c(0, 2),
      religion ~ c(0, 2)
    ),
    percent = "row"
  ) %>%
  modify_header(label = "**Demographic Variable**") %>%
  bold_labels()

# Convert to a flextable for Word export
table_safe_combined <- table3.4.0 %>%
  as_flex_table()

# Save as a Word document
save_as_docx(table3.4.0, path = here("output/table3_4_0.docx"))

table3.4.0
```


##3. 4. 1 Safe of Cholera Vaccine by District and Zone 

```{r}
table3.4.1 <- cholera_data |> 
            select(safe_vaccine,district,zone) %>% 
            tbl_summary(safe_vaccine,
            percent = "row",
            digits = list(
              district~ c(0, 2),
              zone ~ c(0, 2)
            ))


 
table3.4.1 <-  table3.4.1 %>% 
         as_flex_table()


save_as_docx( table3.1.1, path = here("output/table3_4_1.docx"))

table3.4.1


```

## 3. 5. 0 Community Influence decision about vaccination by District and Zone 

```{r}

              


```



## 3. 6. 0 Difficult in access cholera vaccination by Sex, Education and Religion  

```{r}

table3.6.0 <- cholera_data %>%
  select(sex, age_group, level_education, religion, ocv_access) %>%
  tbl_summary(
    by = ocv_access,
    statistic = list(
      sex ~ "{n} ({p}%)",
      age_group ~ "{n} ({p}%)",
      level_education ~ "{n} ({p}%)",
      religion ~ "{n} ({p}%)"
    ),
    digits = list(
      sex ~ c(0, 2),
      age_group ~ c(0, 2),
      level_education ~ c(0, 2),
      religion ~ c(0, 2)
    ),
    percent = "row"
  ) %>%
  modify_header(label = "**Demographic Variable**") %>%
  bold_labels()

# Convert to a flextable for Word export
table_safe_combined <- table3.6.0 %>%
  as_flex_table()

# Save as a Word document
save_as_docx(table3.6.0, path = here("output/table3_6_0.docx"))

table3.6.0





```


## 3. 6. 1 Difficult in access cholera vaccination by District 


```{r}

table3.6.1 <- cholera_data |> 
            select(ocv_prevent_cholera,district) %>% 
            tbl_summary(ocv_prevent_cholera,
            percent = "row",
            digits = list(
              district~ c(0, 2)
            ))


 
table3.6.1 <-  table3.6.1 %>% 
         as_flex_table()


save_as_docx( table3.6.1, path = here("output/table3_6_1.docx"))

table3.6.1

```



##3. 7. 0 OCV status by Sex, Age Group, Education and Religious 

```{r}



```


## 3. 8. 0 Family Members vaccinated by District and Zone 
```{r}
table3.6.1 <- cholera_data |> 
            select(ocv_prevent_cholera,district) %>% 
            tbl_summary(ocv_prevent_cholera,
            percent = "row",
            digits = list(
              district~ c(0, 2)
            ))


 
table3.6.1 <-  table3.6.1 %>% 
         as_flex_table()


save_as_docx( table3.6.1, path = here("output/table3_6_1.docx"))

table3.6.1

```


## 3. 9. 0 Willingness to get vaccinated in the Future OCV by Sex, Age Group and Education 

```{r}

```


## 3. 9. 1 Willingness to get vaccinated in the Future OCV by District and Zone 

```{r}

```


## 3. 10. 0 Recommend a Family member to get vaccinated by District and Zone 

```{r}

```



## 3. 13. 0 Prefer ways to Receive Information about Vaccine by Sex, Age Group and Education and Religious 
```{r}

```



## 3. 13. 1 Prefer ways to Receive Information about Vaccine by District and Zone 

```{r}

```







